Computational methods in landscape ecology

### 2024-09-02 Manuscript.qmd
Update meta information and BIB

---
title: "Computational methods in landscape ecology"
keywords: keyword1, keyword2
author:
  - name: Maximilian H.K. Hesselbarth
    orcid: 0000-0003-1125-9918
    email: mhk.hesselbarth@gmail.com
    affiliations:
      - name: International Institute for Applied Systems Analysis, Biodiversity, Ecology, and Conservation Group, Laxenburg, Austria
    attributes:
      - corresponding: boolean
  - name: Jakub Nowosad
    orcid: 0000-0002-1057-3721
    email: nowosad.jakub@gmail.com
    affiliations:
      - name: Adam Mickiewicz University, Poznan, Poland
      - name: University of Münster, Münster, Germany
  - name: Marti Bosch
    orcid: 0000-0001-8735-9144
    email: marti.bosch@epfl.ch
    affiliations:
      - name: École polytechnique fédérale de Lausanne, Lausanne, Switzerland
  - name: Martin Jung
    orcid: 0000-0002-7569-1390
    email: jung@iiasa.ac.at
    affiliations:
      - name: International Institute for Applied Systems Analysis, Biodiversity, Ecology, and Conservation Group, Laxenburg, Austria
format:
  pdf:
    keep-tex: true
    template-partials: 
      - title.tex
    include-in-header: 
      text: | 
        \usepackage{lineno}\linenumbers
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
papersize: a4paper
fontsize: 10pt
geometry: margin=25mm
indent: 2m
linestretch: 1.5
bibliography: CLER.bib
csl: springer-basic-author-date.csl
---

@@

{{< include Sections/01-introduction.qmd >}}
{{< include Sections/02-spatial-patterns.qmd >}}
{{< include Sections/03-connectivity.qmd >}}
{{< include Sections/05-simulations.qmd >}}
{{< include Sections/08-software.qmd >}}

>>>>

---
title: "Computational methods in landscape ecology"

keywords: keyword1, keyword2

author:
  - name: Maximilian H.K. Hesselbarth
    orcid: 0000-0003-1125-9918
    email: mhk.hesselbarth@gmail.com
    affil-id: 1
    attributes:
      - corresponding: boolean
  - name: Jakub Nowosad
    orcid: 0000-0002-1057-3721
    email: nowosad.jakub@gmail.com
    affil-id: 2,3
  - name: Marti Bosch
    orcid: 0000-0001-8735-9144
    email: marti.bosch@epfl.ch
    affil-id: 4
  - name: Martin Jung
    orcid: 0000-0002-7569-1390
    email: jung@iiasa.ac.at
    affil-id: 1

affiliations: 
  - id: 1
    name: International Institute for Applied Systems Analysis, Biodiversity, Ecology, and Conservation Group, Laxenburg, Austria
  - id: 2
    name: Adam Mickiewicz University, Poznan, Poland
  - id: 3
    name: University of Münster, Münster, Germany
  - id: 4
    name: École polytechnique fédérale de Lausanne, Lausanne, Switzerland

format:
  pdf:
    keep-tex: true
    template-partials: 
      - title.tex
    include-in-header: 
      text: | 
        \usepackage{lineno}\linenumbers
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}

papersize: a4paper
fontsize: 10pt
geometry: margin=25mm
indent: 2m
linestretch: 1.5
number-sections: true

bibliography: CLER.bib
csl: springer-basic-author-date.csl
---

@@

{{< include Sections/01-introduction.qmd >}}
{{< include Sections/02-spatial-patterns.qmd >}}
{{< include Sections/03-connectivity.qmd >}}
{{< include Sections/04-sampling.qmd >}}
{{< include Sections/05-simulations.qmd >}}
{{< include Sections/06-spatial-planning.qmd >}}
{{< include Sections/07-genetics.qmd >}}
{{< include Sections/08-software.qmd >}}
{{< include Sections/09-discussion.qmd >}}
